---
output:
  pdf_document: default
  html_document: default
---

---
  title: "DEEPPD FD-mean"
output:
  pdf_document: default
html_document: default
date: "2024-06-19"
  
```{r, echo = TRUE, results='hide'}
# set the wd to where tsv file is located 
setwd("/projects/jbyambadorj/DEEP_study/data/processed/DEEPPD/mriqc")

# set up 
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(scales)
data <- read.table('group_bold.tsv', header = TRUE, sep="\t")
data.frame(data)
data
```


```{r, echo = TRUE, results = 'hide'}
# select fd_mean column only 

fd_mean_data = select(data, bids_name, fd_mean)

bids_name = pull(fd_mean_data, bids_name)
score = pull(fd_mean_data, fd_mean)


# create new column ses_number 
myvar = c()

for (sub in 2:8) {
  for (j in 1:6) { 
    for (i in 1:4)
    { 
      myvar = c(myvar, c(j))
    }
  }
}

# append extra ses06 to sub04 since it has 5 runs. 

myvar = append(myvar, 6, 72)
fd_mean_data$ses_number = myvar 

fd_mean_data
```


```{r, echo = TRUE, results = 'hide'}

# create new column id which contains run_number in the df 

temp = c()

for (sub_num in 2:8) {
  for (ses_num in 1:6) {
    for (run_num in 1:4) {
      temp = append(temp, paste("0", run_num,
                                sep=""))
    }
  }
}

# correct extra run05 in sub04-ses06
temp = append(temp, "05", 72)
fd_mean_data$run_id = temp

# change run05 of sub05/ses04 (entry 89) into run04
# since run 03 is missing 


```


Script for generating fd_mean vs acq_session plot for sub-CMH-0000002

```{r}

# The following reads off only from sub 02 data. 

slice(fd_mean_data, 1:24) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB02 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 


```


SUB-CMH-0000003 Plot

## SUB-03 is a patient 

```{r}
slice(fd_mean_data, 25:48) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB03 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 

```
SUBJECT 04 FD_MEAN PLOT 
## SUB04 is a patient 
```{r}
slice(fd_mean_data, 49:73) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB04 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 

```
SUB-CMH000005 FD_MEAN PLOT

## SUB-05 is a Patient 

```{r}
slice(fd_mean_data, 74:97) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB05 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 



```

SUB-CMH000006 FD_MEAN PLOT

## Note: Not sure if SUB06 is a patient or control 
```{r}
slice(fd_mean_data, 98:121) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB06 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 



```


CMH-SUB000007 FD_MEAN PLOT

##  CMH-SUB07 is a CONTROL
```{r}
slice(fd_mean_data, 122:145) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB07 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 



```

## CMH-SUB0000008 FD_MEAN PLOT

## Not sure if SUB-08 is a patient or control. 
```{r}
slice(fd_mean_data, 146:169) %>%
  group_by(ses_number) %>%
  ggplot() + 
  geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
  geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                group = ses_number, linetype = as.factor(ses_number)), 
            position = position_dodge(width = 0), lwd = 1.2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB08 FD mean variability across acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 
  
  facet_wrap(facets = "ses_number", nrow = 1, scale = "free_x") 
```




