---
title: "DEEPPi FD mean"
output:
  pdf_document: default
  html_document: default
date: "2024-06-23"
---

```{r, echo = TRUE, results = 'hide', include = FALSE}
# set the wd to where tsv file is located 
setwd("/projects/jbyambadorj/DEEP_study/data/processed/DEEPPi/mriqc")

# uncomment the line to download packages missing 
# install.packages(c("tidyverse", "stringr", "dplyr", "scales"))

# set up 
library(tidyverse, ggplot2)
library(stringr)
library(scales)
library(dplyr)
data <- read.table('group_bold.tsv', header = TRUE, sep="\t")
data.frame(data)
data
```

```{r, echo = TRUE, results = 'hide'}
# select fd_mean column only 

fd_mean_data = select(data, bids_name, fd_mean)

# create new column ses_number 
myvar = c()

for (item in fd_mean_data$bids_name) {
  ses_num = substring(item, 17, 22)

  if (ses_num == "ses-01") {
      myvar = append(myvar, "01")
  }
  else if (ses_num == "ses-02") {
      myvar = append(myvar, "02")
  }
  else if (ses_num == "ses-03") {
    myvar = append(myvar, "03")
  }
  else if (ses_num == "ses-04") {
      myvar = append(myvar, "04")
  }
  else if (ses_num == "ses-05") {
      myvar = append(myvar, "05")
  }
  else {
    myvar = append(myvar, "06")
  }
}

fd_mean_data$ses_number = myvar

```



## set up 
```{r, echo = TRUE, results = 'hide'}
# create new column id which contains run_number in the df 

temp = c()

for (item in fd_mean_data$bids_name) {
  ses_num = substring(item, 34, 39)

  if (ses_num == "run-01") {
      temp = append(temp, "1")
  }
  else if (ses_num == "run-02") {
      temp = append(temp, "2")
  }
  else if (ses_num == "run-03") {
    temp = append(temp, "3")
  }
  else if (ses_num == "run-04") {
      temp = append(temp, "4")
  }
  else if (ses_num == "run-05") {
      temp = append(temp, "5")
  }
  else {
    temp = append(temp, "0")
  }
}

fd_mean_data$run_id = temp

# rename run 0 in sub101/ses03 to run 06 (df entry 109)

fd_mean_data$run_id[109] = "6"


```


## SUB-CMH0000001 FD_MEAN PLOT
## Needs to have 
```{r sub01}

# The following reads off only from sub 01 data. 

slice(fd_mean_data, 1:10) %>%
  group_by(ses_number) %>%
    ggplot() + 
    geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
    geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                  group = ses_number, linetype = as.factor(ses_number)), 
              position = position_dodge(width = 0), lwd = 1.2) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB01 FD mean variability acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 

    facet_wrap(facets = "ses_number", nrow = 1, scales = "free_x") 
  

```

## SUB69 plot is missing session 03.
```{r}

# The following reads off only from sub69 data. 

slice(fd_mean_data, 11:30) %>%
  group_by(ses_number) %>%
    ggplot() + 
    geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
    geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                  group = ses_number, linetype = as.factor(ses_number)), 
              position = position_dodge(width = 0), lwd = 1.2) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB69 FD mean variability acquisitions",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 

    facet_wrap(facets = "ses_number", nrow = 1, scales = "free_x") 
  

```


```{r}

# The following reads off only from sub77 data. 

slice(fd_mean_data, 31:52) %>%
  group_by(ses_number) %>%
    ggplot() + 
    geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
    geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                  group = ses_number, linetype = as.factor(ses_number)), 
              position = position_dodge(width = 0), lwd = 1.2) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB77 FD mean variability across runs",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 

    facet_wrap(facets = "ses_number", nrow = 1, scales = "free_x") 
  

```
## the above plot has very high fd_mean values (from ses03 onward the fd_mean >= 0.4)



## archive/DEEPPi/SUB79/func file structure:

├── sub-CMH00000079_ses-05_task-rest_bold.json
├── sub-CMH00000079_ses-05_task-rest_bold.nii.gz
├── sub-CMH00000079_ses-05_task-rest_run-01_bold.json
├── sub-CMH00000079_ses-05_task-rest_run-01_bold.nii.gz
├── sub-CMH00000079_ses-05_task-rest_run-02_bold.json
├── sub-CMH00000079_ses-05_task-rest_run-02_bold.nii.gz
├── sub-CMH00000079_ses-05_task-rest_run-03_bold.json
├── sub-CMH00000079_ses-05_task-rest_run-03_bold.nii.gz
├── sub-CMH00000079_ses-05_task-rest_run-04_bold.json
└── sub-CMH00000079_ses-05_task-rest_run-04_bold.nii.gz
```{r}

# The following reads off only from sub 79 data. 

slice(fd_mean_data, 53:78) %>%
  group_by(ses_number) %>%
    ggplot() + 
    geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
    geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                  group = ses_number, linetype = as.factor(ses_number)), 
              position = position_dodge(width = 0), lwd = 1.2) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB79 FD mean variability across runs",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 

    facet_wrap(facets = "ses_number", nrow = 1, scales = "free_x") 
  
```

```{r}

# The following reads off only from sub 85 data. 

slice(fd_mean_data, 79:96) %>%
  group_by(ses_number) %>%
    ggplot() + 
    geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
    geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                  group = ses_number, linetype = as.factor(ses_number)), 
              position = position_dodge(width = 0), lwd = 1.2) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB85 FD mean variability across runs",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 

    facet_wrap(facets = "ses_number", nrow = 1, scales = "free_x") 
  
```

```{r}
# The following reads off only from sub 101 data. 

slice(fd_mean_data, 97:120) %>%
  group_by(ses_number) %>%
    ggplot() + 
    geom_point(aes(x = run_id, y = fd_mean, fill = as.factor(ses_number))) +
    geom_line(aes(x = run_id, y = fd_mean, color = as.factor(ses_number), 
                  group = ses_number, linetype = as.factor(ses_number)), 
              position = position_dodge(width = 0), lwd = 1.2) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
    x = "MRI acquisition", 
    y = "FD_mean value", 
    title = "SUB101 FD mean variability across runs",
    color = "session number",
    fill = "session number",
    linetype = "session number") + 

    facet_wrap(facets = "ses_number", nrow = 1, scales = "free_x") 
  
```
